A-maze of Natural Stories: Texts are comprehensible using the Maze task

### 2021-06-23 Papers/Paper/manuscript.Rmd
files to make the manuscript happy

```{r pre-error}
brm_txl_interact <- read_rds(paste0(here(),"/Analysis/brm_txl_interact.rds"))
brm_grnn_interact <- read_rds(paste0(here(),"/Analysis/brm_grnn_interact.rds"))
brm_ngram_interact <- read_rds(paste0(here(),"/Analysis/brm_ngram_interact.rds"))
a <- show_summary(brm_txl_interact) %>% mutate(model="TXL") %>% mutate(Term=str_replace(Term,"txl","surp"))
b <- show_summary(brm_grnn_interact) %>% mutate(model="GRNN") %>% mutate(Term=str_replace(Term,"grnn","surp"))
c <- show_summary(brm_ngram_interact) %>% mutate(model="5-gram") %>% mutate(Term=str_replace(Term,"ngram","surp"))

summ <- a %>% union(b) %>% union(c) %>% pivot_wider(names_from="model", values_from=c(`Estimate`)) %>% 
  mutate(Term=factor(Term, 
                        levels=c("Intercept", 
                                 "surp_center",
                                 "length_center",
                                 "freq_center",
                                 "surp_center:length_center",
                                 "length_center:freq_center",
                                 "past_c_surp",
                                 "past_c_length",
                                 "past_c_freq",
                                 "past_c_surp:past_c_length",
                                 "past_c_length:past_c_freq")
                                 )) %>% 
  arrange(Term) %>% 
  mutate(Term=c("Intercept", "Surprisal", "Length", "Frequency",
                  "Surp x Length", "Freq x Length", "Past Surprisal",
                  "Past Length", "Past Freq", "Past Surp x Length", "Past Freq x Length")) %>% 
  select(Term, `5-gram`, `GRNN`, TXL)

@@

```{r}
d_lm <- labelled_pre_error %>% group_by(word, txl_center, ngram_center, grnn_center, freq_center, length_center,
                                        past_c_txl, past_c_ngram, past_c_grnn, past_c_freq, past_c_length, Word_ID) %>% 
  summarize(mean_rt=mean(rt))

@@

```{r, include=F}
anova(all_surp, txl_only)
anova(all_surp, grnn_only)
anova(all_surp, ngram_only)

@@

```{r read_data}
d.raw.a <- here("Data/SPR/batch1_pro.csv") %>% 
  read_csv()

@@

```{r surprisals}

@@

```{r filter}

@@

```{r pre_gam}
ngram_data <- d.subset %>% select(rt=RT, surprisal=ngram_surp, prev_surp=past_ngram, 
                                            freq=freq_center, len=length_center,
                                            prev_freq=past_c_freq, prev_len=past_c_length
                                            ) %>% mutate(model="5-gram")

@@

```{r prep-brms}
d.for.lm <- d.subset %>%
  mutate(Word_ID=as_factor(str_c(Story_Num, Word_In_Story_Num, sep="_"))) %>% 
  mutate(subject=factor(WorkerId),
         rt=RT) %>% write_rds("for_brms.rds")
```

```{r}
#mean by subject for each word
d.byword <- d.for.lm %>% rename(word=Word) %>% 
  group_by(word, txl_center, ngram_center, grnn_center, freq_center, length_center,
                                        past_c_txl, past_c_ngram, past_c_grnn, past_c_freq, past_c_length, Word_ID) %>% 
  summarize(mean_rt=mean(rt))
```

@@

```{r spr-table}
ngram_only_tidy <- tidy(ngram_only, effects="fixed") %>% mutate(type="5-gram") %>% 
  mutate(term=str_replace(term, "ngram", "surp"))

@@

all_tidy <- ngram_only_tidy %>% union(txl_only_tidy) %>% union(grnn_only_tidy) %>% 
  select(Term=term, estimate, std.error, type) %>% 
  mutate(Ci_high=estimate+1.96*std.error,
         Ci_low=estimate-1.96*std.error,
         Range=str_c(round(estimate,1)," [",round(Ci_low, 1),", ",round(Ci_high,1),"]")) %>% 
  select(Term, type, Range) %>% 
  pivot_wider(id_cols=Term, names_from=type, values_from=Range) %>% 
    mutate(Term=factor(Term, 
                        levels=c("(Intercept)", 
                                 "surp_center",
                                 "length_center",
                                 "freq_center",
                                 "freq_center:length_center",
                                 "past_c_surp",
                                 "past_c_length",
                                 "past_c_freq",
                                 "past_c_freq:past_c_length")
                                 )) %>% 
  arrange(Term) %>% 
  mutate(Term=c("Intercept", "Surprisal", "Length", "Frequency",
                   "Freq x Length", "Past Surprisal",
                  "Past Length", "Past Freq", "Past Freq x Length"))

>>>>

```{r pre-error-prep, eval=F}
brm_txl_interact <- read_rds(paste0(here(),"/Analysis/brm_txl_interact.rds"))
brm_grnn_interact <- read_rds(paste0(here(),"/Analysis/brm_grnn_interact.rds"))
brm_ngram_interact <- read_rds(paste0(here(),"/Analysis/brm_ngram_interact.rds"))
a <- show_summary(brm_txl_interact) %>% mutate(model="TXL") %>% mutate(Term=str_replace(Term,"txl","surp"))
b <- show_summary(brm_grnn_interact) %>% mutate(model="GRNN") %>% mutate(Term=str_replace(Term,"grnn","surp"))
c <- show_summary(brm_ngram_interact) %>% mutate(model="5-gram") %>% mutate(Term=str_replace(Term,"ngram","surp"))

summ <- a %>% union(b) %>% union(c) %>% write_rds(here("Analysis/brms_summary.rds"))

```{r pre-error}
summ <- read_rds(here("Analysis/brms_summary.rds")) %>% pivot_wider(names_from="model", values_from=c(`Estimate`)) %>% 
  mutate(Term=factor(Term, 
                        levels=c("Intercept", 
                                 "surp_center",
                                 "length_center",
                                 "freq_center",
                                 "surp_center:length_center",
                                 "length_center:freq_center",
                                 "past_c_surp",
                                 "past_c_length",
                                 "past_c_freq",
                                 "past_c_surp:past_c_length",
                                 "past_c_length:past_c_freq")
                                 )) %>% 
  arrange(Term) %>% 
  mutate(Term=c("Intercept", "Surprisal", "Length", "Frequency",
                  "Surp x Length", "Freq x Length", "Past Surprisal",
                  "Past Length", "Past Freq", "Past Surp x Length", "Past Freq x Length")) %>% 
  select(Term, `5-gram`, `GRNN`, TXL)

@@

```{r,include=F, eval=F}
d_lm <- labelled_pre_error %>% group_by(word, txl_center, ngram_center, grnn_center, freq_center, length_center,
                                        past_c_txl, past_c_ngram, past_c_grnn, past_c_freq, past_c_length, Word_ID) %>% 
  summarize(mean_rt=mean(rt))

@@

```{r, include=F, eval=F}
anova(all_surp, txl_only)
anova(all_surp, grnn_only)
anova(all_surp, ngram_only)

@@

```{r read_data, eval=F}
d.raw.a <- here("Data/SPR/batch1_pro.csv") %>% 
  read_csv()

@@

```{r surprisals, eval=F}

@@

```{r filter, eval=F}

@@

```{r pre_gam, eval=F}
ngram_data <- d.subset %>% select(rt=RT, surprisal=ngram_surp, prev_surp=past_ngram, 
                                            freq=freq_center, len=length_center,
                                            prev_freq=past_c_freq, prev_len=past_c_length
                                            ) %>% mutate(model="5-gram")

@@

```{r prep-brms, eval=F}
d.for.lm <- d.subset %>%
  mutate(Word_ID=as_factor(str_c(Story_Num, Word_In_Story_Num, sep="_"))) %>% 
  mutate(subject=factor(WorkerId),
         rt=RT) 
```

```{r, eval=F}
#mean by subject for each word
d.byword <- d.for.lm %>% rename(word=Word) %>% 
  group_by(word, txl_center, ngram_center, grnn_center, freq_center, length_center,
                                        past_c_txl, past_c_ngram, past_c_grnn, past_c_freq, past_c_length, Word_ID) %>% 
  summarize(mean_rt=mean(rt))
```

@@

```
```{r spr-prep, eval=F}
ngram_only_tidy <- tidy(ngram_only, effects="fixed") %>% mutate(type="5-gram") %>% 
  mutate(term=str_replace(term, "ngram", "surp"))

@@

all_tidy <- ngram_only_tidy %>% union(txl_only_tidy) %>% union(grnn_only_tidy) %>% write_rds(here("Analysis/SPR_lmer_summ.rds"))
```
```{r spr-table}

all_tidy <- read_rds(here("Analysis/SPR_lmer_summ.rds")) %>% 
  select(Term=term, estimate, std.error, type) %>% 
  mutate(Ci_high=estimate+1.96*std.error,
         Ci_low=estimate-1.96*std.error,
         Range=str_c(round(estimate,1)," [",round(Ci_low, 1),", ",round(Ci_high,1),"]")) %>% 
  select(Term, type, Range) %>% 
  pivot_wider(id_cols=Term, names_from=type, values_from=Range) %>% 
    mutate(Term=factor(Term, 
                        levels=c("(Intercept)", 
                                 "surp_center",
                                 "length_center",
                                 "freq_center",
                                 "freq_center:length_center",
                                 "past_c_surp",
                                 "past_c_length",
                                 "past_c_freq",
                                 "past_c_freq:past_c_length")
                                 )) %>% 
  arrange(Term) %>% 
  mutate(Term=c("Intercept", "Surprisal", "Length", "Frequency",
                   "Freq x Length", "Past Surprisal",
                  "Past Length", "Past Freq", "Past Freq x Length"))
